### 2020-04-12 evaluation/plots/microbenchmarks-table.tex
Add optimized bi-grams plot

\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lllllll}
\toprule
Script ~&~ Structure & Input &Seq Time & Script Size(\todo{20, 100}) &Compile Time (\todo{20, 100}) & Highlights \\
\midrule
\tti{grep} ~&~ $3\times$\tsta & 1~GB & 95.45~s & \todo{\#Commands} & 63.84~ms\qquad 965.11~ms & complex NFA regex \\
\tti{sort} ~&~ $\tsta, \tpur$ & 10~GB & 24.72~s & \todo{\#Commands} & 105.77~ms\qquad 1999.55~ms & \tti{sort}ing \\
\tti{top-n} ~&~ $2\times\tsta, 4\times\tpur$ & 10~GB & 84.18~s & \todo{\#Commands} & 172.39~ms\qquad 3295.23~ms & double \tti{sort}, \tti{uniq} reduction \\
\tti{wf} ~&~ $3\times\tsta, 3\times\tpur$ & 10~GB & 25.75~s & \todo{\#Commands} & 172.83~ms\qquad 3294.47~ms & double \tti{sort}, \tti{uniq} reduction \\
\tti{grep-light} ~&~ $3\times$\tsta & 100~GB & 98.21~s & \todo{\#Commands} & 35.33~ms\qquad 355.90~ms & $3\times$\tsta \\
\tti{spell} ~&~ $4\times\tsta, 3\times\tpur$ & 1~GB & 9.18~s & \todo{\#Commands} & 312.67~ms\qquad 6820.98~ms & comparisons (\tti{comm}) \\
\tti{shortest-scripts} ~&~ $5\times\tsta, 2\times\tpur$ & \todo{UNKNOWN} & 34.40~s & \todo{\#Commands} & 314.23~ms\qquad 6759.41~ms & \todo{extensive file-system operation} \\
\tti{diff} ~&~ \todo{TODO} & 10~GB & 30.69~s & \todo{\#Commands} & 225.73~ms\qquad 4336.29~ms & non-parallelizable \tti{diff}ing \\
\bottomrule
\end{tabular*}

>>>>

\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lllllll}
\toprule
Script ~&~ Structure & Input &Seq Time & Script Size(\todo{20, 100}) &Compile Time (\todo{20, 100}) & Highlights \\
\midrule
\tti{grep} ~&~ $3\times$\tsta & 1~GB & 4809.61~s & \todo{\#Commands} & 63.37~ms\qquad 965.72~ms & complex NFA regex \\
\tti{sort} ~&~ $\tsta, \tpur$ & 10~GB & 1429.04~s & \todo{\#Commands} & 201.12~ms\qquad 2005.70~ms & \tti{sort}ing \\
\tti{top-n} ~&~ $2\times\tsta, 4\times\tpur$ & 10~GB & 4373.79~s & \todo{\#Commands} & 169.50~ms\qquad 3340.67~ms & double \tti{sort}, \tti{uniq} reduction \\
\tti{wf} ~&~ $3\times\tsta, 3\times\tpur$ & 10~GB & 1351.91~s & \todo{\#Commands} & 165.41~ms\qquad 3325.32~ms & double \tti{sort}, \tti{uniq} reduction \\
\tti{grep-light} ~&~ $3\times$\tsta & 100~GB & 98.21~s & \todo{\#Commands} & 35.33~ms\qquad 355.90~ms & $3\times$\tsta \\
\tti{spell} ~&~ $4\times\tsta, 3\times\tpur$ & 1~GB & 481.13~s & \todo{\#Commands} & 311.45~ms\qquad 6655.26~ms & comparisons (\tti{comm}) \\
\tti{shortest-scripts} ~&~ $5\times\tsta, 2\times\tpur$ & \todo{UNKNOWN} & 1706.75~s & \todo{\#Commands} & 305.33~ms\qquad 6729.06~ms & \todo{extensive file-system operation} \\
\tti{diff} ~&~ \todo{TODO} & 10~GB & 1610.09~s & \todo{\#Commands} & 312.08~ms\qquad 4569.23~ms & non-parallelizable \tti{diff}ing \\
\tti{optimized bi-grams} ~&~ $3\times$\tsta, \tpur & 10~GB & 7434.95~s & \todo{\#Commands} & 135.88~ms\qquad 2674.48~ms & optimized version of bigrams \\
\bottomrule
\end{tabular*}
